### 2016-07-06 src/3_TimeSeries.tex
Adding first proposal

\section{Vector error correction model}
Vector error correction model (VECM)  \cite{engle87} describe the joint behaviour of a set of cointegrated I(1) time series \cite{banerjee1993} and can be derived from the simple VAR model.

>>>>

\section{Vector error correction model}\label{sec:vecm}
Vector error correction model (VECM)  \cite{engle87} describe the joint behaviour of a set of cointegrated I(1) time series \cite{banerjee1993} and can be derived from the simple VAR model.
